The Calculus of Linear Constructions

### 2022-01-17 writing/draft7/draft7.tex
draft

\appendix

@@

\begin{theorem}\label{embedding}
  Embedding. For any CLC context $\Gamma$ and CLC terms $m, A$, if there is $\Gamma \vdash_{\scriptscriptstyle \text{CLC}} m : A$, then there is $\erase{\Gamma} \vdash_{\scriptscriptstyle \text{CC$\omega$}} \erase{m} : \erase{A}$.
\end{theorem}
\begin{proof}
  By induction on the derivation of $\Gamma \vdash_{\scriptscriptstyle \text{CLC}} m : A$.
\end{proof}

\begin{corollary}\label{embeddingcontext}
  For any CLC context $\Gamma$, if there is $\Gamma \vdash_{\scriptscriptstyle \text{CLC}}$, then there is $\erase{\Gamma} \vdash_{\scriptscriptstyle \text{CC$\omega$}}$.
\end{corollary}
\begin{proof}
  Direct consequence of applying Theorem \ref{embedding} to all types in context $\Gamma$.
\end{proof}

\begin{theorem}
  Strong normalization of CLC.
\end{theorem}
\begin{proof}
  Suppose there exists a well-typed CLC term $m$ with an infinite sequence of reductions. Theorem \ref{embedding} shows that there must exist some term $\erase{m}$ that is well-typed in CC$\omega$. Additionally, this infinite sequence of reductions on $m$ can be translated in CC$\omega$ step-wise by Lemma \ref{erasestep}. This shows that we have constructed a non-normalizing CC$\omega$ term $\erase{m}$, which a contradiction to the strong normalization property of CC$\omega$, thus CLC must be strongly normalizing as well.
\end{proof}

\subsection{Embedding of CC$\omega$}
To show that CLC is compatible with the predicative fragment of CC$\omega$, we construct a lifting procedure that lifts CC$\omega$ terms into CLC in a straightforward way.
\begin{align*}
  \lift{x}                     & = x                                        \\
  \lift{Type_i}                & = U_i                                      \\
  \lift{(x : A) \rightarrow B} & = (x \utype \lift{A}) \rightarrow \lift{B} \\
  \lift{\lambda x : A.n}       & = \lambda x\utype\lift{A}.\lift{n}         \\
  \lift{m\ n}                  & = \lift{m}\ \lift{n}
\end{align*}

>>>>

\appendix
\appendixname

@@

\begin{theorem}\label{embed}
  Embedding. For any CLC context $\Gamma$ and CLC terms $m, A$, if there is $\Gamma \vdash_{\scriptscriptstyle \text{CLC}} m : A$, then there is $\erase{\Gamma} \vdash_{\scriptscriptstyle \text{CC$\omega$}} \erase{m} : \erase{A}$.
\end{theorem}
\begin{proof}
  By induction on the derivation of $\Gamma \vdash_{\scriptscriptstyle \text{CLC}} m : A$.
\end{proof}

\begin{corollary}\label{embeddingcontext}
  For any CLC context $\Gamma$, if there is $\Gamma \vdash_{\scriptscriptstyle \text{CLC}}$, then there is $\erase{\Gamma} \vdash_{\scriptscriptstyle \text{CC$\omega$}}$.
\end{corollary}
\begin{proof}
  Direct consequence of applying Theorem \ref{embed} to all types in context $\Gamma$.
\end{proof}

\begin{theorem}
  Strong normalization of CLC.
\end{theorem}
\begin{proof}
  Suppose there exists a well-typed CLC term $m$ with an infinite sequence of reductions. Theorem \ref{embed} shows that there must exist some term $\erase{m}$ that is well-typed in CC$\omega$. Additionally, this infinite sequence of reductions on $m$ can be translated in CC$\omega$ step-wise by Lemma \ref{erasestep}. This shows that we have constructed a non-normalizing CC$\omega$ term $\erase{m}$, which a contradiction to the strong normalization property of CC$\omega$, thus CLC must be strongly normalizing as well.
\end{proof}

\subsection{Embedding}
To show that CLC is compatible with the predicative fragment of CC$\omega$, we construct a lifting procedure that lifts CC$\omega$ terms into CLC in a straightforward way.
\begin{align*}
  \lift{x}                     & = x                                        \\
  \lift{Type_i}                & = U_i                                      \\
  \lift{(x : A) \rightarrow B} & = (x \utype \lift{A}) \rightarrow \lift{B} \\
  \lift{\lambda x : A.n}       & = \lambda x\utype\lift{A}.\lift{n}         \\
  \lift{m\ n}                  & = \lift{m}\ \lift{n}
\end{align*}
